---
title: "CrossActivePassive V1 Analysis"
author: "Martin Zettersten"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(
                prompt  = FALSE,
                cache   = FALSE,
                echo = TRUE,
                warning=F,
                message=F)
```

```{r load packages and data, include=FALSE}
library(tidyverse)
library(here)
library(cowplot)
library(lme4)
theme_set(theme_cowplot())
```

## Read in data

```{r}
## read in data
d <- read_csv(here("data","version1","processed_data","crossActivePassive_v1_processed_data.csv"))
```

## Sampling {.tabset}

Summarize subject-level data.

```{r}
## Active selections
subj_sample_active <- d %>%
  filter(trialType=="selection"&round_condition=="active") %>%
  group_by(subject,round_condition) %>%
  summarize(
    prop_ambiguous=mean(choiceItemCondition=="ambiguous")
  )

sample_active_overall <- subj_sample_active %>%
  group_by(round_condition) %>%
  summarize(
    N=n(),
    mean_ambiguous=mean(prop_ambiguous),
    sd_ambiguous=sd(prop_ambiguous),
    ci_ambiguous=qt(0.975, N-1)*sd_ambiguous/sqrt(N),
    mean_ambiguous_lower_ci=mean_ambiguous-ci_ambiguous,
    mean_ambiguous_upper_ci=mean_ambiguous+ci_ambiguous
  )

##Passive selections
subj_sample_passive <- d %>%
  filter(trialType=="selection"&round_condition=="passive") %>%
  group_by(subject,round_condition) %>%
  summarize(
    prop_ambiguous_1=mean(randomItemCondition1=="ambiguous"),
    prop_ambiguous_2=mean(randomItemCondition2=="ambiguous"),
  ) %>%
  mutate(
    prop_ambiguous=(prop_ambiguous_1+prop_ambiguous_2)/2
  )

sample_passive_overall <- subj_sample_passive %>%
  group_by(round_condition) %>%
  summarize(
    N=n(),
    mean_ambiguous=mean(prop_ambiguous),
    sd_ambiguous=sd(prop_ambiguous),
    ci_ambiguous=qt(0.975, N-1)*sd_ambiguous/sqrt(N),
    mean_ambiguous_lower_ci=mean_ambiguous-ci_ambiguous,
    mean_ambiguous_upper_ci=mean_ambiguous+ci_ambiguous
  )
```

### Active Condition Plot

```{r}
ggplot(subj_sample_active,aes(round_condition,prop_ambiguous))+
  geom_bar(data=sample_active_overall,aes(y=mean_ambiguous),stat="identity",width=0.3,fill="red",alpha=0.5,color="black")+
  geom_errorbar(data=sample_active_overall,aes(y=mean_ambiguous,ymin=mean_ambiguous_lower_ci,ymax=mean_ambiguous_upper_ci),width=0)+
  geom_dotplot(stackdir="center",binaxis="y",alpha=0.6,dotsize=0.5)+
  geom_hline(yintercept=0.5, linetype="dashed")+
  ylab("Proportion of Ambiguous Selections")+
  xlab("Condition")
```

### Passive Condition Plot

```{r}
ggplot(subj_sample_passive,aes(round_condition,prop_ambiguous))+
  geom_bar(data=sample_passive_overall,aes(y=mean_ambiguous),stat="identity",width=0.3,fill="red",alpha=0.5,color="black")+
  geom_errorbar(data=sample_passive_overall,aes(y=mean_ambiguous,ymin=mean_ambiguous_lower_ci,ymax=mean_ambiguous_upper_ci),width=0)+
  geom_dotplot(stackdir="center",binaxis="y",alpha=0.6,dotsize=0.5)+
  geom_hline(yintercept=0.5, linetype="dashed")+
  ylab("Proportion of (Random) Ambiguous Selections")+
  xlab("Condition")
```

### Model (Active condition)

```{r}
d$ambiguous_selection <- ifelse(d$choiceItemCondition=="ambiguous",1,0)
m <- glmer(ambiguous_selection ~ 1  + (1|subject)+ (1|choiceImage), data=filter(d,trialType=="selection"&round_condition=="active"), family=binomial)
summary(m)
```

Robustness checks:

```{r}
t.test(subj_sample_active$prop_ambiguous,mu=0.5)
wilcox.test(subj_sample_active$prop_ambiguous,mu=0.5)
```

## Test Performance {.tabset}

Summarize subject-level performance

```{r}
subj_test_by_condition <- d %>%
  filter(trialType=="test") %>%
  group_by(subject,condition,round_condition) %>%
  summarize(
    round_n=n(),
    accuracy=mean(isRight, na.rm=TRUE)
  )

test_by_condition <- subj_test_by_condition %>%
  group_by(round_condition) %>%
  summarize(
    N=n(),
    mean_accuracy=mean(accuracy),
    sd_accuracy=sd(accuracy),
    ci_accuracy=qt(0.975, N-1)*sd_accuracy/sqrt(N),
    lower_ci=mean_accuracy-ci_accuracy,
    upper_ci=mean_accuracy+ci_accuracy
  )

test_by_condition_by_order <- subj_test_by_condition %>%
  group_by(condition,round_condition) %>%
  summarize(
    N=n(),
    mean_accuracy=mean(accuracy),
    sd_accuracy=sd(accuracy),
    ci_accuracy=qt(0.975, N-1)*sd_accuracy/sqrt(N),
    lower_ci=mean_accuracy-ci_accuracy,
    upper_ci=mean_accuracy+ci_accuracy
  )
```

### Plot test performance

```{r}
ggplot(subj_test_by_condition,aes(round_condition,accuracy, color=round_condition,fill=round_condition))+
  geom_bar(data=test_by_condition,aes(y=mean_accuracy),stat="identity",width=0.3,alpha=0.5,color="black")+
  geom_errorbar(data=test_by_condition,aes(y=mean_accuracy,ymin=lower_ci,ymax=upper_ci),width=0,color="black")+
  geom_dotplot(stackdir="center",binaxis="y",alpha=0.6,dotsize=0.5,color="black",fill="black")+
  geom_hline(yintercept=1/8, linetype="dashed")+
  ylab("Test Accuracy")+
  xlab("Condition")+
  theme(legend.position="none")
```

### Model

```{r}
d <- d %>%
  mutate(
    condition_centered = case_when(
      round_condition=="active" ~ 0.5,
      round_condition=="passive" ~ -0.5,
      TRUE ~ NA_real_))
m <- glmer(isRight ~ 1 + condition_centered + (1+condition_centered|subject)+ (1|choiceImage), data=filter(d,trialType=="test"), family=binomial)
summary(m)
```

## Sampling-Test correlations {.tabset}

```{r}
subj_sampling_test <- subj_sample_active %>%
  bind_rows(subj_sample_passive) %>%
  left_join(subj_test_by_condition)
```

### Plot Correlations

```{r}
ggplot(subj_sampling_test,aes(prop_ambiguous,accuracy,color=round_condition))+
  geom_violin(aes(group=prop_ambiguous),draw_quantiles=c(0.5),trim=T)+
  geom_jitter(width=0.02)+
  theme(legend.position="none")+
  geom_smooth(method="lm")+
  facet_wrap(~round_condition)
```

### Test Correlations

Active condition

```{r}
cor.test(filter(subj_sampling_test,round_condition=="active")$prop_ambiguous,filter(subj_sampling_test,round_condition=="active")$accuracy)
```
Passive condition

```{r}
cor.test(filter(subj_sampling_test,round_condition=="passive")$prop_ambiguous,filter(subj_sampling_test,round_condition=="passive")$accuracy)
```

### Exploratory: Test Interaction

```{r}
d <- d %>%
  left_join(subj_sampling_test)
m <- glmer(isRight ~ prop_ambiguous * condition_centered+(1+condition_centered|subject)+(1|choiceImage), data=filter(d,trialType=="test"), family=binomial)
summary(m)
```

Test Active condition by centering model on active condition

```{r}
#shift condition coding (centered on active condition)
d <- d %>%
  mutate(
    condition_active = case_when(
      round_condition=="active" ~ 0,
      round_condition=="passive" ~ -1,
      TRUE ~ NA_real_))
m_active <- glmer(isRight ~ prop_ambiguous * condition_active+(1+condition_active|subject)+(1|choiceImage), data=filter(d,trialType=="test"), family=binomial)
summary(m_active)
```

Test Passive condition by centering model on passive condition

```{r}
#shift condition coding (centered on passive condition)
d <- d %>%
  mutate(
    condition_passive = case_when(
      round_condition=="active" ~ 1,
      round_condition=="passive" ~ 0,
      TRUE ~ NA_real_))
m_passive <- glmer(isRight ~ prop_ambiguous * condition_passive+(1+condition_passive|subject)+(1|choiceImage), data=filter(d,trialType=="test"), family=binomial)
summary(m_passive)
```

## Does Sampling Preference predict subject-level accuracy differences?

```{r}
subj_sampling_test_diff <- subj_sampling_test %>%
  ungroup() %>%
  group_by(subject, condition) %>%
  summarize(
    accuracy_diff=accuracy[round_condition=="active"]-accuracy[round_condition=="passive"],
    prop_ambiguous_active=prop_ambiguous[round_condition=="active"],
    prop_ambiguous_passive=prop_ambiguous[round_condition=="passive"],
    prop_ambiguous_diff=prop_ambiguous_active-prop_ambiguous_passive
  )

## plot relationships
pA <- ggplot(subj_sampling_test_diff,aes(prop_ambiguous_active,accuracy_diff))+
  geom_jitter()+
  geom_smooth(method="lm")+
  xlab("Proportion Ambiguous Selections\nin Active Condition")+
  ylab("Accuracy Difference Active - Passive")
pB <- ggplot(subj_sampling_test_diff,aes(prop_ambiguous_diff,accuracy_diff))+
  geom_jitter()+
  geom_smooth(method="lm")+
  xlab("Difference in Ambiguous Selections\nActive-Passive")+
  ylab("Accuracy Difference Active - Passive")
plot_grid(pA,pB)
```

